### 2022-10-19 RR-9418.tex
meow

%% url
\usepackage{url}
%% maths
\usepackage{amsmath,amssymb,amsthm,bm}
%% \usepackage{amsfonts}

%% algorithms
\usepackage{algorithmicx}
\usepackage[ruled, linesnumbered, noend]{algorithm2e}

@@

%% tables
\usepackage{booktabs}
\usepackage{multirow}
%% figures
%\usepackage{caption}
\usepackage{subfig}
\usepackage{tikz}
\usetikzlibrary{decorations.pathreplacing,plotmarks,shapes,matrix}
%% transform eps in pdf crossplateform
\usepackage{epstopdf}
\usepackage{epsfig}

\usepackage{xspace}

@@

\newtheorem{problem}{Problem Statement}
\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\newcommand{\eventually}{\square\,}
\newcommand{\ie}{{i.e.,}\xspace}
\newcommand{\eg}{{e.g.,}\xspace}

@@

@@

\RRdate{September 2021}
% \RRVersion{2}
% \RRdater{<Another date for version 2>}
\RRauthor{
  Adrien L{\`e}bre
  %%  \thanks[aff1]{Inria}
  \and
  Brice N{\'e}delec
  %% \thanksref{aff1}
  \and
  Alexandre Van Kempen
  %% \thanksref{aff1}
}
\authorhead{L{\`e}bre, N{\'e}delec, Van Kempen}
\RRtitle{\NAME : Confiner le trafic de l'indexation décentralisée de contenu au niveau du Edge} %% titre français long
\titlehead{\NAME : Confiner le trafic de l'indexation décentralisée de contenu au niveau du Edge} %% titre français court
\RRetitle{\NAME: Lock Down the Traffic of Decentralized Content Indexing at the Edge}

@@

@@

\RRNo{9418}
\makeRR

>>>>

%% url
\usepackage{url}
%% maths
\usepackage{amsmath,amssymb,amsthm,bm,centernot}
%% \usepackage{amsfonts}

%% algorithms
\usepackage{algorithmicx}
\usepackage[ruled, linesnumbered, noend]{algorithm2e}
\usepackage{multicol}

@@

%% tables
\usepackage{booktabs, tabularx, multirow}
%% figures
%\usepackage{caption}
\usepackage{subfig}
\usepackage{tikz}
\usetikzlibrary{decorations.pathreplacing,plotmarks,shapes,matrix}
%% transform eps in pdf crossplateform
\usepackage{epstopdf}
\usepackage{epsfig}

\usepackage{xspace}
\usepackage{pifont}% http://ctan.org/pkg/pifont
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%

@@

\newtheorem{problem}{Problem Statement}
\newtheorem{definition}{Definition}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\newcommand{\eventually}{\square\,}
\newcommand{\ie}{{i.e.,}\xspace}
\newcommand{\eg}{{e.g.,}\xspace}

@@

\newcommand{\SCALE}{1} %% used in figures, forces renewcommand for consistent behavior

@@

\RRdate{September 2021}
% \RRVersion{2}
% \RRdater{<Another date for version 2>}
\RRauthor{
  Adrien L{\`e}bre
  %%  \thanks[aff1]{Inria}
  \and
  Brice N{\'e}delec
  %% \thanksref{aff1}
  \and
  Alexandre Van Kempen
  %% \thanksref{aff1}
}
\authorhead{L{\`e}bre, N{\'e}delec, Van Kempen}
\RRtitle{\NAME : Confiner le trafic de l'indexation décentralisée de contenu au niveau du Edge} %% titre français long

\titlehead{\NAME : Lock Down the Traffic of Decentralized Content Indexing at the Edge}
\RRetitle{\NAME: Lock Down the Traffic of Decentralized Content Indexing at the Edge}

@@

\RRnote{\TODO{This preprint has not undergone peer review (when
    applicable) or any post-submission improvements or
    corrections. The Version of Record of this contribution is
    published in [insert volume title], and is available online at
    https://doi.org/[insert DOI]}}

%% \RRnote{This version of the contribution has been accepted for
%%   publication, after peer review (when applicable) but is not the
%%   Version of Record and does not reflect post-acceptance improvements,
%%   or any corrections. The Version of Record is available online at:
%%   http://dx.doi.org/[insert DOI]. Use of this Accepted Version is
%%   subject to the publisher’s Accepted Manuscript terms of use
%%   \url{https://www.springernature.com/gp/open-research/policies/accepted-manuscript-terms}}

@@

\RRNo{9418}

\makeRR

### 2022-10-19 input/figdel.tex
toward camera ready

\begin{figure}[t]
  \newcommand{\SCALE}{0.8}

@@

  \newcommand\INVISIBLESPACING{1.6}
  \newcommand\ADD{\alpha}
  \newcommand\DEL{\delta}

@@

  \begin{center}
    \subfloat[Part A][\label{fig:delA}$a$ deletes its partition. It
      notifies all \processes that belong to its
      partition.]{\input{input/figdelA.tex}}
    \hspace{3pt}
    \subfloat[Part B][\label{fig:delB}$\delta$ stops when it encounters
      another partition. $b$ answers with its partition.]{\input{input/figdelB.tex}}
    \hspace{3pt}
    \subfloat[Part C][\label{fig:delC}$a$ receives, delivers, and forwards the message $\alpha_d^3$.
      Every node belongs to $P_d$.]{\input{input/figdelC.tex}}
  \end{center}
  \caption{\label{fig:del}Efficient removal of a partition using
    scoped broadast.} % $a$ eventually acknowledges that it belongs to $P_d$ with $\alpha_d^3$ echoing.}
\end{figure}

>>>>

\begin{figure}[t]
  \renewcommand{\SCALE}{0.8}

@@

  \newcommand\INVISIBLESPACING{1.55}
  \newcommand\ADD{\alpha}
  \newcommand\DEL{\delta}

@@

  \begin{center}
    \subfloat[Part A][\label{fig:delA}$a$ deletes its partition. It
      notifies all \processes that belong to its
      partition.]{\input{input/figdelA.tex}}
    \hspace{3pt}
    \subfloat[Part B][\label{fig:delB}$\delta$ stops when it encounters
      another partition. $b$ answers with its partition.]{\input{input/figdelB.tex}}
    \hspace{3pt}
    \subfloat[Part C][\label{fig:delC}$a$ receives, delivers, and forwards the message $\alpha_d^3$.
      Every node belongs to $P_d$.]{\input{input/figdelC.tex}}
  \end{center}
  \caption{\label{fig:del}Efficient removal of a partition using
    scoped broadcast.} % $a$ eventually acknowledges that it belongs to $P_d$ with $\alpha_d^3$ echoing.}
\end{figure}

### 2022-10-19 input/figproblem.tex

\begin{figure*}
  \begin{center}
    \subfloat[Part A][\label{fig:problemA}Both \Process~$a$ and
      \Process~$d$ add then delete their partition. For the recall,
      $w_{ab} = 2$; $w_{bc} = w_{bd} = 1$; $w_{cd} =
      3$.]{\input{input/figproblemA.tex}}
    \hspace{0pt}
    \subfloat[Part B][\label{fig:problemB}$b$
      delivers and forwards the $\alpha$ message about $P_a$ while
      \Process~$c$ delivers and forwards both $\alpha$ and $\delta$
      messages about $P_d$.]  {\input{input/figproblemB.tex}}
    \hspace{0pt}
    \subfloat[Part C][\label{fig:problemC}$b$
      already blocks the propagation of $\delta_a$ despite it
      propagated $\alpha_a$ before; and $c$ does not deliver
      $\alpha_d$, for it already deleted it
      before.]{\input{input/figproblemC.tex}}
    \hspace{0pt}
    \subfloat[Part D][\label{fig:problemD}\Processes
      discard remaining messages. Since $b$ cannot deliver
      $\delta_a$, $c$ and $d$ remain in the deleted $P_a$.]
             {\input{input/figproblemD.tex}}
  \end{center}
  \caption{\label{fig:problem}Naive propagation of $\alpha$ and
    $\delta$ messages is insufficient to guarantee consistent partitioning.}
\end{figure*}

>>>>

\begin{figure*}
  \begin{center}
    \subfloat[Part A][\label{fig:problemA}Both nodes $a$ and $d$ create a
      new partition.  $w_{ab} = 2$; $w_{bc} = w_{bd} = 1$; $w_{cd} =
      3$.]{\input{input/figproblemA.tex}}
    \hspace{0pt}
    \subfloat[Part B][\label{fig:problemB}Both $a$ and $d$ delete
      their partition. $b$ delivers and forwards $\alpha_a$ while
      $c$ delivers and forwards both $\alpha_d$ and $\delta_d$.]
             {\input{input/figproblemB.tex}}
    \hspace{0pt}
    \subfloat[Part C][\label{fig:problemC}$b$
      already blocks the propagation of $\delta_a$ despite it
      propagated $\alpha_a$ before; and $c$ does not deliver
      $\alpha_d$, for it already deleted it
      before.]{\input{input/figproblemC.tex}}
    \hspace{0pt}
    \subfloat[Part D][\label{fig:problemD}\Processes
      discard remaining messages. Since $b$ cannot deliver
      $\delta_a$, $c$ and $d$ remain in the deleted $P_a$.]
             {\input{input/figproblemD.tex}}
  \end{center}
  \caption{\label{fig:problem}Naive propagation of $\alpha$ and
    $\delta$ messages is insufficient to guarantee consistent partitioning.}
\end{figure*}

### 2022-10-19 input/introduction.tex

The data storage paradigm shifted from centralized in
the cloud to distributed at the edges of the network. 
% There is an ongoing evolution of storing data from the cloud to the
% edges of the network.
This change aims at keeping the data close to
\begin{inparaenum}[(i)]
\item its producers since data may be too expensive or sensitive to be
  transmitted through the network; and
\item its consumers so data may quickly and efficiently reach
  them~\cite{cachier,foggy_cache,shi2016edge}.
\end{inparaenum}
%% It avoids transmitting Either because it is where it has been
%% created and it is too expensive to be transmitted through the
%% network, or because it has been replicated to bring data closer to
%% the end users ~\cite{shi2016edge, foggy_cache, cachier}.
%
To favour this transition, new designs for data management across Edge
infrastructures have been investigated~\cite{confais2017object,confais2017performance,fogstore,hasenburg2020towards}.  They
enable strategies to confine traffic by writing data locally and
replicating content according to effective needs. However, locating
content remains challenging. Retrieving a content location may
actually take more time than retrieving the content itself.
%% Although
%% these systems, provide good properties such as favouring network
%% traffic confinement by writting data locally and replicating contents
%% according to the effective needs, determining the location where to
%% get the content might be more expensive than retrieving the content
%% itself.
%
Indeed, these systems, when not using a centralized index hosted in a
Cloud, rely on \underline{d}istributed \underline{h}ash
\underline{t}ables (DHT) spread across different \processes composing
the infrastructure~\cite{maymounkov2002kademlia}. When a client wants
to access specific content, it requests a remote \process to provide
at least one \process identity to retrieve this content from. After
retrieving the content, the client can create another replica to
improve the performance of future accesses, but it must recontact the
indexing service to notify of the creation of this new replica.
%% a local replica is created to improve the performance for future
%% accesses and the process in charge of maintaining the index is
%% contacted once again to reflect this new location.
%

@@

\item [$\bullet$] We provide an implementation entitled \NAME that
  uses aforementioned principles to \underline{a}dapt its partitioning
  to creations and deletions of partitions even in dynamic systems
  where \nodes can join, leave, or crash at any time. \NAME's
  efficiency relies on a communication primitive called
  \underline{s}coped-broad\underline{cast}
   that enables epidemic
  dissemination of messages as long as receiving \processes verify an
  application-dependant predicate.

>>>>

The data storage paradigm shifted from centralized in
the cloud to distributed at the edges of the network. 
% There is an ongoing evolution of storing data from the cloud to the
% edges of the network.
This change aims at keeping the data close to
\begin{inparaenum}[(i)]
\item its producers since data may be too expensive or sensitive to be
  transmitted through the network; and
\item its consumers so data may quickly and efficiently reach
  them~\cite{cachier,foggy_cache,shi2016edge}.
\end{inparaenum}
%% It avoids transmitting Either because it is where it has been
%% created and it is too expensive to be transmitted through the
%% network, or because it has been replicated to bring data closer to
%% the end users ~\cite{shi2016edge, foggy_cache, cachier}.
%
To favor this transition, new designs for data management across Edge
infrastructures have been investigated~\cite{confais2017object,confais2017performance,fogstore,hasenburg2020towards}.  They
enable strategies to confine traffic by writing data locally and
replicating content according to effective needs. However, locating
content remains challenging. Retrieving a content location may
actually take more time than retrieving the content itself.
%% Although
%% these systems, provide good properties such as favouring network
%% traffic confinement by writting data locally and replicating contents
%% according to the effective needs, determining the location where to
%% get the content might be more expensive than retrieving the content
%% itself.
%
Indeed, these systems, when not using a centralized index hosted in a
Cloud, rely on \underline{d}istributed \underline{h}ash
\underline{t}ables (DHT) spread across different \processes composing
the infrastructure~\cite{maymounkov2002kademlia}. When a client wants
to access specific content, it requests a remote \process to provide
at least one \process identity to retrieve this content from. After
retrieving the content, the client can create another replica to
improve the performance of future accesses, but it must recontact the
indexing service to notify of the creation of this new replica.
%% a local replica is created to improve the performance for future
%% accesses and the process in charge of maintaining the index is
%% contacted once again to reflect this new location.
%

@@

\item [$\bullet$] We provide an implementation entitled \NAME that
  uses aforementioned principles to \underline{a}dapt its partitioning
  to creations and deletions of partitions even in dynamic systems
  where \nodes can join, leave, or crash at any time. \NAME's
  efficiency relies on a communication primitive called
  \underline{s}coped-broad\underline{cast}
   that enables epidemic
  dissemination of messages as long as receiving \processes verify an
  application-dependent predicate.

### 2022-10-19 input/tablerelatedwork.tex

\begin{table}[t]
  \scriptsize
  \centering
  \caption{\label{table:relatedwork}Related work summary.}
  \begin{tabularx}{\columnwidth}{@{}lcccc@{}}
  \toprule

  Approaches & \multirow{2}{5em}{\centering Without Third-party} & Update & \multirow{2}{3.5em}{Eventually Consistent} & \multirow{2}{5em}{\centering\underline{R}eactive or \underline{C}yclic} \\
  \\
  \midrule

>>>>

\begin{table}[t]
  \scriptsize
  \centering
  \caption{\label{table:relatedwork}Related work summary.}
  \begin{tabularx}{\columnwidth}{@{}lcccc@{}}
  \toprule
  Approaches & Without Third-party & Update & Eventually Consistent & \underline{R}eactive or \underline{C}yclic \\
  \midrule
